A thesis draft

### 2018-11-20 res/sections/08-Background.tex
Add part on SFC proxy and other considerations

\section{Service Function Chaining}
The Service Function Chaining (SFC) concept was defined 
in~\cite{halpern2015service} and refers to an ordered set of Service Functions
(SF) and the constraint, defined after a classification process, to packets and
flows. SF are the particular functions whose aim is the treatment of packets
received. They can work on different levels of the network layer. These
components can be implemented as virtual element or a combination of a physical
network element and the software running on the top of it. There are no
limitations on the number of SFs running on the same network element, so in
general it is possible to have one or more functions running on the same
element. SFs can be aware or not that are part of a certain chain, in the
matter case they are called \emph{SFC aware} functions, in the latter one \emph
SFC unaware}.

@@

\todo{add sfc proxy}

@@

\subsection{Considerations}

>>>>

\section{Service Function Chaining}
The Service Function Chaining (SFC) concept was defined 
in~\cite{halpern2015service} and refers to an ordered set of Service Functions
(SF) and the constraint, defined after a classification process, to packets and
flows. SF are the particular functions whose aim is the treatment of packets
received. They can work on different levels of the network layer. These
components can be implemented as virtual element or a combination of a physical
network element and the software running on the top of it. 
There are no limitations on the number of SFs running on the same network
element, so in general it is possible to have one or more functions running on
the same element. SFs can be aware or not that are part of a certain chain, in
the matter case they are called \emph{SFC aware} functions, in the latter one
\emph{SFC unaware}.

The lifecycle management of the chain is enabled by two emerged technologies,
software defined networking and network defined
virtualization~\cite{medhat2017service}.

@@

This encapsulation is neither supported from SFC unaware SF nor from legacy 
SF\footnote{Legacy SF refers to network function created before SFC framework}
so \emph{SFC Proxies} has to be included in this ecosystem. These components
sits the SFF and the SFs. They accept packets from the SFF and remove the
encapsulation before delivering the packet to the SFs. In a mirrored way, it
receive the result of the SF and reapplies the SFC header, in order to be
managed by the SFF and the overall system. The communication among SFFs and
proxies is the same as the SFFs and SFC aware SF.

@@

\subsection{Other considerations}
In this architecture the SFs are viewed are resource and managed by the control
plane. Capabilities, availability and location are all accountable to the
control part as their creation. It is also in charge of collecting information
needed by the classifier to make proper decisions. The control plane could be
either distributed or centralized and even a combination is possible.

SFC system add to the original packets information as a NSH, that both contains
metadata and information on the path that it must traverse. It is possible that
the size of the packet, in this manner, exceed the MTU on some link in the
chain. Solution must take in account this problem and the cost to overcome it.
